Men and Women Both Prefer and Perceive Inaction as More Competent

### 2024-02-16 outputs/paper/paper.qmd
paper update

Yachun Qian, Yoshiyuki Takimoto, Lu Wang and Akira Yasumura’s journal article “Exploring cultural and gender differences in moral judgment: A cross-cultural study based on the CNI model” in *Current Psychology* examined if there was a difference in moral judgment between cultures and gender. Focusing specifically on the gender aspects of their research, they found that women were more sensitive to having their moral judgment influenced by moral norms as ascribed by their respective culture, similar to the conclusions made by Bertram et al. However, they concluded that action versus inaction preference did not differ significantly across gender, rather between cultures [@culturepaper]. Valerio Capraro and Jonathan Sippel’s article “Gender differences in moral judgment and the evaluation of gender-specified moral agents'' in *Cognitive Processing* also investigated the responses of moral dilemmas such as the traditional trolley paradigm which found that research participants did not feel differently to how a person should act in a moral dilemma based on the gender of a moral agent [@genderpaper]. These differences in results across all three papers indicate that the field does not yet have a consensus on whether or not there are differences in decision-making between genders.

@@

This report takes the data from the Study 2 from “Evaluations of Action and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes: Inaction Agents Are Preferred to and Perceived as More Competent and Normative Than Action Agents” to examine if there are differences in moral judgment between gender. The estimands of interest from the data set are preference and perceived competence between action and inaction agents by gender. Data was taken from the *Center for Open Science* and published directly by Fillion, Strauch, and Feldman. To examine whether or not there are differences in preferences and perceived competence of different decision-making actions between gender, graphical analysis was conducted to visualize the responses of study participants. Summary statistics in addition to t-test and p-values calculated in order to discern if the differences in responses were of statistical significance. Report findings reveal that there are no statistical differences in the preference and perceived competence between gender which could indicate that there are other factors aside from gender that influence moral judgment preferences.

>>>>

@@

This report takes the data from the Study 2 from “Evaluations of Action and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes: Inaction Agents Are Preferred to and Perceived as More Competent and Normative Than Action Agents” to examine if there are differences in moral judgment between gender. The estimands of interest from the data set are preference and perceived competence between action and inaction agents by gender. Data was taken from the *Center for Open Science* and published directly by Fillion, Strauch, and Feldman. To examine whether or not there are differences in preferences and perceived competence of different decision-making actions between gender, graphical analysis was conducted to visualize the responses of study participants. Summary statistics were calculated to discern if the differences in responses were of statistical significance. Report findings reveal that there are no statistical differences in the preference and perceived competence between gender which could indicate that there are other factors aside from gender that influence moral judgment preferences.
